Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-07-13 AM+draft.tex
13July v1

 A replicate was analysed via the different methods as follows. All programs/packages were run at their default settings. 
 The Eagle package and MLMM script were the easiest of the programs/packages to implement. 
 Their results are immediately 
 interpretable. Their findings are the set of SNPs in strongest association with the trait. Each 
SNP in this set identifies a separate genomic region of interest, whose position is given by the map location of the SNP.

BigRR, LMM-Lasso, and glmnet  implement regression-based 
regularisation methods. Coefficient estimates of the SNP from fitting all loci simultaneously are reported. However, for these results to be useable, the statistical significance of a
SNP in the model is also required.  The statistical significance rather than the coefficient size of a SNP is a better measure of the strength of evidence for a SNP-trait association. 
Calculating the significance of effects within these regularisation methods is challenging. We resort to 
stability selection, a sampling approach that allows us to calculate 
the statistical significance of the 
SNP empirically (see Methods for details). This does increase the computational burden of implementing these methods for genome-wide association mapping.

>>>>

 A replicate was analysed as follows. All programs/packages were run at their default settings. 
 The Eagle package and MLMM script were the easiest of the programs/packages to implement. 
 Their results are immediately 
 interpretable. Their findings are the set of SNPs in strongest association with the trait. Each 
SNP in this set identifies a separate genomic region of interest, whose position is given by the map location of the SNP.  
Implementing BigRR, LMM-Lasso, and glmnet required more work. 
The computer programs/packages are based on regularisation methods. Being able to fit all the SNPs simultaneously within a regression 
framework is their strength. The analytical challenges of calculating p-values due to the adaptive nature of the estimation procedure is their 
weakness.  To solve this problem, at the cost of increased computation, we calculated the significance of a SNP empirically via stability selection (see Methods). R2VIM is an R package that implements random forests.  
We were required to 
specify the minimum size of a terminal node, the number of trees, and number of potential variables 
for building a tree.
